Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-03-21 paper/paper.qmd
Updated code  uner assumption

@@

**Repeated Measures ANOVA**
(To be changed)
When performing a repeated measures ANOVA, it is essential to verify that the underlying assumptions of the test are met. These assumptions include:
\begin{itemize}
    \item \textbf{Normality}: The dependent variable should be normally distributed within each group.
    \item \textbf{Sphericity}: The variances of the differences between all combinations of related groups should be equal.
    \item \textbf{Homogeneity of Variance}: The variances of the dependent variable should be equal across groups.
\end{itemize}

>>>>

## Model

$$
\text{memory\_game\_score}_i = \beta_0 + \beta_1 \cdot \text{drug}_i + \beta_2 \cdot \text{dosage\_level}_i + \beta_3 \cdot (\text{drug}_i \times \text{dosage\_level}_i) + \varepsilon_i
$$

Where:

- $\beta_0$ is the intercept.

- $\beta_1$, $\beta_2$, and $\beta_3$ are coefficients for the predictors and interaction term.

- $\varepsilon_i$ is the random error term.

```{r}

# Regression Model results
anova_model <- lm(memory_game_score ~ drug * dosage_level, data = clean_data)
summary(anova_model)

$$
Y_{ijk} = \mu + \alpha_i + \beta_j + (\alpha\beta)_{ij} + \varepsilon_{ijk}
$$

Where:

- $Y_{ijk}$: Memory score
- $\mu$: Overall mean  
- $\alpha_i$: Effect of the $i^{\text{th}}$ drug  
- $\beta_j$: Effect of the $j^{\text{th}}$ dosage level  
- $(\alpha\beta)_{ij}$: Interaction effect between drug and dosage  
- $\varepsilon_{ijk} \sim \mathcal{N}(0, \sigma^2)$: Random error

```{r}
# Two way ANOVA result
anova(anova_model)
```
```{r}
# Normality Check
ggqqplot(residuals(anova_model)) + ggtitle("Q-Q Plot of Residuals")
# Shapiro-Wilk Normality Test
shapiro_test <- shapiro.test(residuals(anova_model))
shapiro_test
```

```{r}
# Scale-Location Plot
plot(anova_model, which = 3)
```
```{r}
# Perform Bartlett’s test for homogeneity of variance
bartlett_test <- bartlett.test(memory_game_score ~ interaction(drug, dosage_level), data = clean_data)

# Display test results
bartlett_test
```

@@

**Two Way ANOVA**
(To be changed)
When performing a repeated measures ANOVA, it is essential to verify that the underlying assumptions of the test are met. These assumptions include:
\begin{itemize}
    \item \textbf{Normality}: The dependent variable should be normally distributed within each group.
    \item \textbf{Sphericity}: The variances of the differences between all combinations of related groups should be equal.
    \item \textbf{Homogeneity of Variance}: The variances of the dependent variable should be equal across groups.
\end{itemize}
